\documentclass{standalone}
% run the following command: pdflatex --shell-escape scenario.tex
\RequirePackage{shellesc}
\usepackage{dot2texi}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\begin{document}
\hyphenation{mee-kij-ken ver-nie-tigd ver-nie-tigt door-stu-ren blijft be-die-nen ver-wij-de-ren media-viewer inci-dent be-kijkt cen-tra-list}
\begin{dot2tex}[dot]
digraph G {                                             
d2toptions ="--autosize"
rankdir=TB
node    [shape="box" lblstyle="text width=7cm,align=left"]

"1" [texlbl="1. A developer changes the Ampersand compiler on his laptop. He does this in a local feature branch of the repo Ampersandtarski/Ampersand to avoid interference with the ongoing development.",color="black"]
"2" [texlbl="2. A developer copies the file .example.env on his laptop to .env to secure safe internal passwords",color="yellow"]
"3" [texlbl="3. A developer edits the file .env on his laptop  to secure safe internal passwords",color="yellow"]
"4" [texlbl="4. The developer builds an image ampersandtarski/ampersand:local on his laptop  for local testing only. Danger: do not push this image to docker hub!",color="black"]
"5" [texlbl="5. The developer pushes a change to Github from his local feature branch to the remote feature branch to submit the change for automated testing and to share his progress with the team.",color="black"]
"6" [texlbl="6. The developer does a pull request  on Github in the repo Ampersandtarski/Ampersand, stating that the change is ready for peer testing.",color="black"]
"7" [texlbl="7. Github merges the change on Github into the development branch. ",color="black"]
"8" [texlbl="8. Github generates the image ampersandtarski/ampersand:development onto Docker hub  to share the image with the rest of the world.",color="black"]
"9" [texlbl="9. A developer changes the Prototype framework on his laptop in a local feature branch of the repo Ampersandtarski/Prototype. ",color="red"]
"10" [texlbl="10. The developer pushes a change to Github from his local feature branch to the remote feature branch for sharing.",color="red"]
"11" [texlbl="11. The developer does a pull request  on Github in the repo Ampersandtarski/Prototype, stating that the change is ready for peer testing.",color="red"]
"12" [texlbl="12. Github merges the change on Github into the development branch. ",color="red"]
"13" [texlbl="13. Github builds the image ampersandtarski/prototype-framework on Github.  ",color="red"]
"14" [texlbl="14. A developer changes  RAP on his laptop in a local feature branch of the repo Ampersandtarski/RAP. ",color="blue"]
"15" [texlbl="15. The developer pushes a change to Github from his local feature branch to the remote feature branch for sharing.",color="blue"]
"16" [texlbl="16. The developer does a pull request  on Github in the repo Ampersandtarski/RAP, stating that the change is ready for peer testing.",color="blue"]
"17" [texlbl="17. Github merges the change on Github into the master branch. ",color="blue"]
"18" [texlbl="18. The developer builds the image ampersandtarski/ampersand-rap:2021-10-22 on his laptop in the repo Ampersandtarski/RAP. ",color="blue"]
"19" [texlbl="19. The developer connects  to a server  for deploying remotely under TLS (https).",color="blue"]
"23" [texlbl="23. A developer changes  Enroll on his laptop in a local feature branch of the repo Ampersandtarski/RAP/Demos/Enroll. ",color="green"]
"24" [texlbl="24. The developer pushes a change to Github from his local feature branch to the remote feature branch for sharing.",color="blue"]
"25" [texlbl="25. The developer builds Enroll on his laptop  ",color="green"]
"26" [texlbl="26. The developer pushes the image ampersandtarski/enroll to Docker hub in ampersandtarski to allow remote deployment of RAP.",color="green"]
"29" [texlbl="29. A developer changes the student prototype configuration on his laptop in a local feature branch of the repo Ampersandtarski/RAP/RAP4USER. ",color="blue"]
"30" [texlbl="30. The developer builds the image ampersandtarski/rap4-student-prototype on his laptop  to allow remote deployment of RAP.",color="blue"]
"31" [texlbl="31. The developer pushes the image ampersandtarski/rap4-student-prototype to Docker hub in ampersandtarski to allow remote deployment of RAP.",color="blue"]
"32" [texlbl="32. The developer records the changed version number of the Ampersand compiler to Github in the development branch of the repo Ampersandtarski/Prototype, to inform the Prototype repo of a compiler upgrade.",color="red"]
"33" [texlbl="33. The Ampersand core team approves the pull request on Github in Ampersandtarski/Prototype to prevent accidents.",color="red"]
"34" [texlbl="34. The Ampersand core team (periodically) releases a new version of the prototype framework on Github into the master branch to share the release with the world.",color="red"]
"35" [texlbl="35. The developer records the changed version number of the Prototype framework to Github in the development branch of the repo Ampersandtarski/RAP, to inform the RAP repo of a compiler upgrade.",color="blue"]
"36" [texlbl="36. The RAP team approves the pull request on Github in Ampersandtarski/RAP to prevent accidents.",color="blue"]
"38" [texlbl="38. The developer ensures that Rap/RAP4/Dockerfile contains `COPY --from ampersandtarski/ampersand:local ...`  on his laptop  to try it locally.",color="blue"]
"39" [texlbl="39. The Ampersand core team approves the pull request on Github in Ampersandtarski/Ampersand to prevent accidents.",color="black"]
"40" [texlbl="40. The Ampersand core team releases a new version of the Ampersand compiler on Github into the master branch of Ampersandtarski/Ampersand. ",color="black"]
"41" [texlbl="41. The Ampersand core team approves the change on Github in Ampersandtarski/Prototype to prevent accidents.",color="red"]
"42" [texlbl="42. Prototype copies a specific release of Ampersand in its image its image   to control the version of Ampersand it uses.",color="red"]
"43" [texlbl="43. RAP copies the development version of Ampersand in its image (see RAP/RAP/Dockerfile)   to control the version of Ampersand it uses.",color="blue"]
"44" [texlbl="44. Github pushes the image ampersandtarski/prototype-framework to Docker hub  for sharing.",color="red"]
"45" [texlbl="45. A developer installs Git on his laptop  for downloading source code.",color="yellow"]
"46" [texlbl="46. A developer installs Docker on his laptop  to get ready for installing RAP.",color="yellow"]
"47" [texlbl="47. The developer clones RAP on his laptop on ~/git/RAP (or choose a location) to load the source code locally.",color="yellow"]
"51" [texlbl="51. The developer creates  a proxy network on his laptop  that is required in `docker-compose.yml`.",color="yellow"]
"52" [texlbl="52. The developer spins up RAP on his laptop  to make RAP work on localhost",color="blue"]
"53" [texlbl="53. The developer navigates  in a browser on his laptop to `localhost` to see the RAP installation page",color="blue"]
"54" [texlbl="54. The developer clicks the red `Reinstall application` button   to create a database for RAP.",color="yellow"]
"55" [texlbl="55. The developer clicks the `home` icon   to see the RAP landing page.",color="blue"]
"56" [texlbl="56. The developer sets permissions for the docker socket on his laptop  to grant the rap4 container access to docker for running prototypes.",color="yellow"]
"57" [texlbl="57. The developer sets `DISABLE\_DB\_INSTALL` to `true` in file `.env`   to prevent accidents when using RAP.",color="yellow"]
"59" [texlbl="59. A developer installs Docker on the server  to get ready for installing RAP.",color="yellow"]
"61" [texlbl="61. The developer creates  a proxy network on the server  that is required in `docker-compose.yml`.",color="yellow"]
"62" [texlbl="62. The developer spins up RAP on the server  to make RAP work on the server",color="blue"]
"63" [texlbl="63. The developer navigates  in a browser on his laptop to the server URL, e.g. rap.cs.ou.nl to see the RAP installation page",color="blue"]
"68" [texlbl="68. The developer clones Prototype on his laptop on ~/git/Prototype (or choose a location) to load the source code locally.",color="yellow"]
"70" [texlbl="70. The developer clones Ampersand on his laptop on ~/git/Ampersand (or choose a location) to load the source code locally.",color="yellow"]
"71" [texlbl="71. The developer pushes the image ampersandtarski/ampersand-rap:2021-10-22 to Docker hub in ampersandtarski to allow remote deployment of RAP.",color="blue"]

{rank=same; 1; 9; 14; 23}

"70" -> "1"
"47" -> "2"
"2" -> "3"
"1" -> "4"
"1" -> "5"
"5" -> "6"
"39" -> "7"
"7" -> "8"
"68" -> "9"
"9" -> "10"
"10" -> "11"
"41" -> "12"
"34" -> "13"
"42" -> "13"
"47" -> "14"
"14" -> "15"
"15" -> "16"
"24" -> "16"
"35" -> "16"
"36" -> "17"
"17" -> "18"
"3" -> "18"
"38" -> "18"
"43" -> "18"
"44" -> "18"
"46" -> "18"
"31" -> "18"
"26" -> "18"
"47" -> "23"
"23" -> "24"
"29" -> "24"
"23" -> "25"
"25" -> "26"
"47" -> "29"
"29" -> "30"
"30" -> "31"
"40" -> "32"
"12" -> "33"
"33" -> "34"
"32" -> "34"
"44" -> "35"
"16" -> "36"
"4" -> "38"
"6" -> "39"
"7" -> "40"
"11" -> "41"
"40" -> "42"
"8" -> "43"
"13" -> "44"
"45" -> "47"
"46" -> "51"
"18" -> "52"
"51" -> "52"
"52" -> "53"
"53" -> "54"
"63" -> "54"
"54" -> "55"
"52" -> "56"
"62" -> "56"
"54" -> "57"
"19" -> "59"
"59" -> "61"
"71" -> "62"
"61" -> "62"
"62" -> "63"
"45" -> "68"
"45" -> "70"
"18" -> "71"
}
\end{dot2tex}                                               
\end{document}
